Normal States Training for High Accuracy Event Detection

### 2016-07-15 paper/ieeeFormat.tex
before coling

\title{Normal States Training for High Accuracy Event Detection}

\maketitle
\begin{abstract}
In the news value theory, the \textit{news unexpectedness} expects the journalists to report the events that are different from the routine things, a.k.a., the normal states. 
For human being, normal states are knowledge learned from news streams and the external environment, and can describe what happened and help to identify what is happening.
In this paper, we propose \textsc{NSDetector}, a high accuracy event detection method that trains normal states better by using knowledge base, which can be treated as the accumulation of happened things. 
%TODO
In \textsc{NSDetector}, 1) balanced for effectiveness and efficiency, normal states are trained as topical words and their chi-squared scores, and initialized by knowledge base; 2) topical word frequencies on targeted corpus within the time window are learned by NS-Prior-LDA, using the normal states as prior; 3) events are detected by monitoring the change of topical word frequencies; 4) normal states are further maintained by detected events incrementally.
Experiments on the benchmark \textit{Edinburgh twitter corpus (30 million tweets)} validate the effectiveness of our proposed \textsc{NSDetector}.
%\textsc{NSDetector} imitates this process automatically in the event detection task, and further verify that the key to improve the accuracy of event detection lies in training the normal states well. 
\end{abstract}

@@

\section{Proposed Method}
\begin{algorithm}
\caption{Overview of \textsc{NSDetector}}
\label{alg:overviewNSDetector}
\KwIn{Knowledge Base's structure \(G^{(0)}\), \(G^{(1)}\), and content \(G^{(2)}\), }
\KwOut{Events}
\(n_{k,t}\)=number of connected component in \(\mathcal{G}_{k,t}\)\\
\For{\(n \in \{ n_{k,t}, \cdots, |\mathcal{G}_{k,t}|\}\) }{
    \(\mathcal{C}_{k,t}=SpectralClustering(\mathcal{G}_{k,t},n)\)\\
    \If{\(min_{i\in \{1,\cdots,n\}} Density(\mathcal{C}_{k,t,i},\mathcal{G}_{k,t})>\tau\)}{
        return \(\mathcal{C}_{k,t}\)
    }
}
\end{algorithm}

\subsection{Initialization of Normal States}
In this part, we discuss in detail how to initialize the normal states from the given knowledge base. 
\begin{algorithm}
\caption{Normal States' Initialization from Knowledge Base}
\label{alg:normalStatesInit}

\KwIn{Taxonomy's Directed Acyclic Graph \(G^{(0)}\), Category-Page Bipartite Graph \(G^{(1)}\), Page-Content Bipartite Graph \(G^{(2)}\), topic related category node \(c\)}
\KwOut{Normal states \(\bm{f}_c\) on topic \(c\)}
\(Pages(c)\leftarrow \varnothing\)\\
\(SuccessorNodes(c) \leftarrow \) Breadth-first-search(\(G^{(0)},c\))\\
\For{\(node \in SuccessorNodes(c)\)}{
    \(Pages(c) \leftarrow Pages(c) \cup G^{(1)}.neighbours(node)\)\\
}
\(WordFrequencyTable(c) \leftarrow \) do word count on the text contents of \(Pages(c)\) \\
\(WordFrequencyTable(All) \leftarrow \) do word count on the text contents of all pages in \(G^{(2)}\).\\
\For{word \(w\) in WordFrequencyTable(All).keys()}{
    \(\tau_{c,w} \leftarrow \) \(w\)'s chi-square score on \(WordFrequencyTable(c)\) and \(WordFrequencyTable(All)\).
}
\Return{\(\bm{f}_c\)}
\end{algorithm}

@@

\ \ Our theme modeling, want to learn the first \(k\) topics with Wikipedia Article \(k\) topics as close as possible, and we will be Wikipedia article \(k\) before 1000 words) was added to the theme of the word frequency word in the subject a priori distribution on the.
Learning to be the first \(k\) Subject polynomial distribution of the word, referred to as \(\phi_k \), Wikipedia article \(k \) distribution of topics for \(\tau_k \), then this formalized process is expressed as: \(\ \phi_k \sim Dir(\beta + \tau_k) \).
Formal presentation of the explanation is: With prior knowledge \(\tau_k \) after the theme \(\phi_k \) is no longer simply rely on symmetric priori \(\beta \), different words right is not the same weight , such as a discussion of "fashion" theme in Wikipedia, it will refer to "dress", "grand", "blue", "gold" and other words, with the asymmetric priori \(\beta + \tau_k \) after in microblogging "fashion" theme "dress" the proportion will be increased in this way so that microblogging corpus theme tends to Wikipedia topic.
\(\tau_k \) in the first \(v \) words such as formula (\ref{eq: wikiPrior}).
Where \(S_k \) as a set of candidate words: high-quality information to use Wikipedia, we extract the theme \(phi_k \ \) in the higher-word word frequency candidate set \(S_k \).
We can control set \(S_k \) in size, the size of the control is usually set for 1000.
The number of frequency \(n_{kv} \) for the word \(v \) (\ k) appears in the Wikipedia article themes of: (\ref{wikiPrior eq}).
If the word \(v \) does not appear in the candidate set \(S_k \), and then set a priori knowledge \(\tau_{kv} = 0 \), otherwise, the word frequency is proportional to \(n_{kv} \) with the prior knowledge of weight \(W\).
In the latter experiment, we will be on a priori knowledge of weights \(W \) will be discussed.

@@

\subsection{Detecting Events from Normal States}
The state of attention of social issue k at time t in cyberspace is binary, namely at the peak or not at the peak. We denote it by hidden binary variable sk,t, which is 1 or 0. We do the inference for the hidden variable sk,t according to Poisson distribution according to Reference10,11. If the state of attention of social issue k at time t is "not at peak", then the probability density function is 
\(p([Ax_(k,t) ]|s_(k,t)=0)=e^(-μ_0 )  μ_0^([Ax_(k,t)])/([Ax_(k,t)]!)\) otherwise the probability density function is \(p([Ax_(k,t) ]|s_(k,t)=1)=e^(-μ_1 )  μ_1^([Ax_(k,t)])/([Ax_(k,t)])\)
In the above functions the symbol \(x_{k,t}\) denotes the attention of social issue k at time t , the symbol A denotes the constant, \(μ_0\) and \(μ_1\) represent the average of \([Ax_(k,t)]\) at peak and not at peak respectively. The state sk,t is inferred from \(ratio=p([Ax_(k,t) ]|s_(k,t)=0)/p([Ax_(k,t) ]|s_(k,t)=1) \).
In calculation, we use the log ratio to determine whether the attention is at peak as in equation (1). logratio>0 indicates that the attention of social issue k at time t is not at peak, otherwise at peak. As the attention xk,t is often between 0.01% and 5% in our experiment, we set the constant A in log ratio equation to be〖10〗^4。
	\(logratio=-(μ_0-μ_1 )+[Ax_(k,t)](log⁡μ_0 -log⁡μ_1)\)
After the data preprocessing, we get the air pollution state sequence\((a_t)_(t=1,…T)\) and the attention state sequence of each social issue \((s_(k,t))_(t=1,…,T;k=1…n)\), where T denotes the number of time windows.

\begin{algorithm}
\caption{Spectral Clustering Based Event Phrase Extraction}
\label{alg:eventKeywordsSearchMethod}
\KwIn{\(\mathcal{B}_{k,t},\mathcal{G}_{k,t},\rho\)}
\KwOut{\(\mathcal{C}_{k,t}\)}
\(n_{k,t}\)=number of connected component in \(\mathcal{G}_{k,t}\)\\
\For{\(n \in \{ n_{k,t}, \cdots, |\mathcal{G}_{k,t}|\}\) }{
    \(\mathcal{C}_{k,t}=SpectralClustering(\mathcal{G}_{k,t},n)\)\\
    \If{\(min_{i\in \{1,\cdots,n\}} Density(\mathcal{C}_{k,t,i},\mathcal{G}_{k,t})>\rho\)}{
        return \(\mathcal{C}_{k,t}\)
    }
}
\end{algorithm}

@@

As shown in Figure \ref{fig: windowsBurstyWordGraph} below, we will one area, a hot word of the time window and hot words between to diagram.
Hot words set \(\ mathcal{B}_{k, t} \) formed in FIG using \textbf{hot word graph} \(\mathcal {G}_{k, t} = (\mathcal{B}_{k, t}, \mathcal{E}_{k, t}) \) indicates,
\(\mathcal{E}_{k, t} = \{(a, b) | a \in \mathcal{B}_{k, t}, b \in \mathcal {B} _ {k, t }, PMI (\mathcal{D}_{k, t}, a, b)> 0 \} \), where \(PMI (\mathcal{D}_{k, t}, a, b) \) the field \(k \) time window \(t \) related microblog \(\ mathcal {D} _ {k, t} \) on the word \(a \) and the word \(b \) point metric information between each other.
% Refer to bursty.py getSimGraph () function

Given a field \(k \) and the time window \(t \), in which the number of events can not be determined in advance.
The two most extreme situations are: events coarse granularity, said the event is equal to the number of Figure \(\ mathcal {G} _ {k, t} \) in the number of connected components; events finer granularity display, event number equal to \(\ mathcal {G} _ {k, t} \) the number of points.
To do this, we use the Density to the degree of density of quantum graphs \(2 \#Edge / (\# Node \ cdot (\# Node-1)) \), the more the greater if the edge density in the range of Density in \((0,1] \).
Density can be a good indicator to determine the size indicates the event: too many unrelated phrases to put together an event can not be represented, too fine particle size, such as a single word can represent only part of the event; only in close co-occurrence of the phrase to a reasonable It indicates that the event granularity.
To this end, we have designed events phrase search algorithm \ ref {alg: eventKeywordsSearchMethod}: We try to find a reasonable number of spectral clustering Clustering \(n \), let \(n \) from a smaller value ( event corresponds to coarser granularity representation) to start the search, then the most likely cluster cluster size is too large, its performance is the clustering results in one or more small Density indicators; continue to increase the number of clusters \(n \), the event represents reduced size, reduced the size of clusters of clusters, thus making the Density index increases; when all cluster clustering Density indicators are larger than the threshold \(\tau \), the search terminates, returning clustering results \(\mathcal{C}_{k, t}\).
As the above process algorithm \ref{alg: eventKeywordsSearchMethod} description line 2 to line 5, we use in practice \(\tau = 0.6 \).
We call \(\mathcal{C}_{k, t} \) results in each cluster to cluster \textbf{event} phrase.

\textbf{detected events related to micro-blog}
\ \
By algorithm \ref{alg:eventKeywordsSearchMethod} find art \(k \) time window \ \(t \) within the \(| \mathcal{C}_{k, t} | \) events phrase later, you can also further find each event and the corresponding event phrase microblogging.
We looked at the first \(i \) events phrase \(\mathcal{C}_{k, t, i} \),
The phrase based on the number of elements distinguish the event, there are three situations: (1) the phrase event more than two hot words, he said while the event is not a phrase between any two words We have a very strong relationship between the co-occurrence, so just pay attention to the co-occurrence relationship stronger side; (2) event phrase has two hot words; (3) the event is only a hot word in the phrase.
Weibo text length is shorter, not all of the microblogging event will include the phrase \(\mathcal{C}_{k, t, i} \) in all the words.
Such as those on "Apple released the new system mac os lion" event, the event phrase "mac", "os", "lion" does not need to appear in all of the micro-Bo, just check the co-occurrence of a strong relationship between the two words appear together whether in an article in the field \(k \) time window \(t \) micro-Bo: If there is, then added to the events related to the collection \(\ mathcal {D} _ {k, t, i} \) in.
For the case of a third cluster cluster contains only a hot word, we only need to identify areas \(k \) contains the hot word of all micro-blog, and add the event to the relevant set \(\ mathcal{D }_{k, t, i} \) in.
Ultimately, we can get the field \(k \) next time window \(t \) in the event the phrase relating to events microblogging \(\{(\mathcal{C}_{k, t, i}, \mathcal{D}_{k, t, i}) \}_{i=1}^{| \mathcal{C}_{k, t} |} \).

>>>>

%主动感知的
\title{Normal States Training for High Accuracy Event Detection}

\maketitle
\begin{abstract}
In the news value theory, the \textit{news unexpectedness} expects the journalists to report the events that are different from the routine things, a.k.a., the normal states. 
For human being, normal states are knowledge learned from news streams and the external environment, and can describe what happened and help to identify what is happening.
In this paper, we propose \textsc{NSDetector}, a high accuracy event detection method that trains normal states better by using knowledge base, which can be treated as the accumulation of happened things. 
%TODO
In \textsc{NSDetector}, 1) a new data structure \textit{normal states} is proposed to restore what happened; 2) \textit{normal states} can be initialized by knowledge base and further updated by upcoming text streams via our proposed probabilistic model NS-Prior-LDA; 3) events can be detected by normal states with high accuracy.
Experiments on the benchmark \textit{Edinburgh twitter corpus (30 million tweets)} validate the effectiveness of our proposed \textsc{NSDetector}.
%\textsc{NSDetector} imitates this process automatically in the event detection task, and further verify that the key to improve the accuracy of event detection lies in training the normal states well. 
\end{abstract}

@@

\section{Proposed Method}
\begin{table}
\begin{tabular}{|p{0.1\columnwidth}|p{0.8\columnwidth}|} \hline
\(G^{(0)}\) & Taxonomy's Graph in Knowledge Base\\ \hline
\(G^{(1)}\) & Category-Page Bipartite Graph in Knowledge Base\\ \hline
\(G^{(2)}\) & Page-Content Bipartite Graph in Knowledge Base\\ \hline
\(c\) & topic related category node in \(G^{(0)}\) and \(G^{(1)}\) \\ \hline
\(K_{\bm{KB}}\) & number of pre-defined topics by Knowledge Base \\ \hline
\(f_{c,w}\) & word \(w\)'s normal state (chi-square score) in category \(c\) \\ \hline
\(\lambda\) & normal state weight in  NS-Prior-LDA\\ \hline
\(\tau_{c,w}\) & word \(w\)'s prior knowledge confidence for topic \(c\) in NS-Prior-LDA\\ \hline
\(S_c\) & topic \(c\)'s all normal states related words \\ \hline
\(K\) & number of topics in NS-Prior-LDA such as \(K>K_{\bm{KB}}\)\\ \hline
\(\mathcal{B}_{c, t}\)  & hot words set detected from topic \(k\) at time \(t\)  \\ \hline
\(\mathcal{G}_{c, t}\)  & hot word graph constructed from \(\mathcal{B}_{c, t}\) \\ \hline
\(\mathcal{C}_{c,t,i}\) & event \(i\)-th related words in topic \(c\) at time \(t\) \\ \hline
\(\mathcal{D}_{c,t,i}\) & event \(i\)-th related tweets in topic \(c\) at time \(t\) \\ \hline
\(\rho\) & density threshold for the sub-graph constructed by event words  \\ \hline

\end{tabular}
\label{symbolsInModel}
\end{table}

\subsection{Initialization of Normal States}
In this part, we discuss in detail how to initialize the normal states from the given knowledge base. 
\begin{algorithm}
\caption{Normal States Initialization from Knowledge Base}
\label{alg:normalStatesInit}

\KwIn{Taxonomy's Graph \(G^{(0)}\), Category-Page Bipartite Graph \(G^{(1)}\), Page-Content Bipartite Graph \(G^{(2)}\), topic related category node \(c\)}
\KwOut{Normal states \(\bm{f}_c\) on topic \(c\)}
\(Pages(c)\leftarrow \varnothing\)\\
DAG \(G^{(0)'} \leftarrow\) Remove Cycles of \(G^{(0)}\) by nodes' HITS-PageRank scores. \\
\(SuccessorNodes(c) \leftarrow \) Breadth-first-traverse(\(G^{(0)},c\))\\
\For{\(node \in SuccessorNodes(c)\)}{
    \(Pages(c) \leftarrow Pages(c) \cup G^{(1)}.neighbours(node)\)\\
}
\(WordFrequencyTable(c) \leftarrow \) do word count on the text contents of \(Pages(c)\) \\
\(WordFrequencyTable(All) \leftarrow \) do word count on the text contents of all pages in \(G^{(2)}\).\\
\For{word \(w\) in WordFrequencyTable(All).keys()}{
    \(\tau_{c,w} \leftarrow \) \(w\)'s chi-square score on \(WordFrequencyTable(c)\) and \(WordFrequencyTable(All)\).
}
\Return{\(\bm{f}_c\)}
\end{algorithm}

@@

\ \ Our theme modeling, want to learn the first \(k\) topics with Wikipedia Article \(k\) topics as close as possible, and we will be Wikipedia article \(k\) before 1000 words) was added to the theme of the word frequency word in the subject a priori distribution on the.
Learning to be the first \(k\) Subject polynomial distribution of the word, referred to as \(\phi_k \), Wikipedia article \(k \) distribution of topics for \(\tau_k \), then this formalized process is expressed as: \(\ \phi_k \sim Dir(\beta + \tau_k) \).
Formal presentation of the explanation is: With prior knowledge \(\tau_k \) after the theme \(\phi_k \) is no longer simply rely on symmetric priori \(\beta \), different words right is not the same weight , such as a discussion of "fashion" theme in Wikipedia, it will refer to "dress", "grand", "blue", "gold" and other words, with the asymmetric priori \(\beta + \tau_k \) after in microblogging "fashion" theme "dress" the proportion will be increased in this way so that microblogging corpus theme tends to Wikipedia topic.
\(\tau_k \) in the first \(v \) words such as formula (\ref{eq: wikiPrior}).
Where \(S_k \) as a set of candidate words: high-quality information to use Wikipedia, we extract the theme \(\phi_k \ \) in the higher-word word frequency candidate set \(S_k \).
We can control set \(S_k \) in size, the size of the control is usually set for 1000.
The number of frequency \(n_{kv} \) for the word \(v \) (\ k) appears in the Wikipedia article themes of: (\ref{wikiPrior eq}).
If the word \(v \) does not appear in the candidate set \(S_k \), and then set a priori knowledge \(\tau_{kv} = 0 \), otherwise, the word frequency is proportional to \(n_{kv} \) with the prior knowledge of weight \(W\).
In the latter experiment, we will be on a priori knowledge of weights \(W \) will be discussed.

@@

\subsection{Detecting Events from Normal States}
The state of attention of social issue k at time t in cyberspace is binary, namely at the peak or not at the peak. We denote it by hidden binary variable \(s_{k,t}\), which is 1 or 0. We do the inference for the hidden variable \(s_{k,t}\) according to Poisson distribution according to Reference\cite{Diao:2012wj} 10,11. If the state of attention of social issue k at time t is "not at peak", then the probability density function is 
\(p(x_{k,t}|s_{k,t}=0)=e^{-\mu_0 }  \frac{\mu_0^{x_{k,t}}}{x_{k,t}!}\) otherwise the probability density function is \(p(x_{k,t}|s_{k,t}=0)=e^{-\mu_1 }  \frac{\mu_1^{x_{k,t}}}{x_{k,t}!}\)
In the above functions the symbol \(x_{k,t}\) denotes the attention of social issue \(k\) at time \(t\) , the symbol A denotes the constant, \(\mu_0\) and \(\mu_1\) represent the average of \(x_{k,t}\) at peak and not at peak respectively. The state \(s_{k,t}\) is inferred from \(ratio=\frac{p(x_{k,t} |s_{k,t}=0)}{p(x_{k,t} |s_{k,t}=1)} \).
In calculation, we use the log ratio to determine whether the attention is at peak as in equation (\ref{eq:logratio}). \(\log ratio>0 \) indicates that the attention of social issue \(k\) at time \(t\) is not at peak, otherwise at peak. 
\begin{equation}
\label{eq:logratio}
\log ratio=-(\mu_0-\mu_1 )+x_{k,t}(\log \mu_0 -\log⁡ \mu_1)
\end{equation}

\begin{algorithm}
\label{alg:eventKeywordsSearchMethod}
\caption{Spectral Clustering Based Event Phrase Extraction}
\label{alg:eventKeywordsSearchMethod}
\KwIn{\(\mathcal{B}_{k,t},\mathcal{G}_{k,t},\rho\)}
\KwOut{\(\mathcal{C}_{k,t}\)}
\(n_{k,t}\)=number of connected component in \(\mathcal{G}_{k,t}\)\\
\For{\(n \in \{ n_{k,t}, \cdots, |\mathcal{G}_{k,t}|\}\) }{
    \(\mathcal{C}_{k,t}=SpectralClustering(\mathcal{G}_{k,t},n)\)\\
    \If{\(min_{i\in \{1,\cdots,n\}} Density(\mathcal{C}_{k,t,i},\mathcal{G}_{k,t})>\rho\)}{
        return \(\mathcal{C}_{k,t}\)
    }
}
\end{algorithm}

@@

As shown in Figure \ref{fig: windowsBurstyWordGraph} below, we will one area, a hot word of the time window and hot words between to diagram.
Hot words set \(\mathcal{B}_{k, t} \) formed in FIG using \textbf{hot word graph} \(\mathcal{G}_{k, t} = (\mathcal{B}_{k, t}, \mathcal{E}_{k, t}) \) indicates,
\(\mathcal{E}_{k, t} = \{(a, b) | a \in \mathcal{B}_{k, t}, b \in \mathcal{B}_{k, t }, PMI (\mathcal{D}_{k, t}, a, b)> 0 \} \), where \(PMI (\mathcal{D}_{k, t}, a, b) \) the field \(k \) time window \(t \) related microblog \(\mathcal{D}_{k, t} \) on the word \(a\) and the word \(b\) point metric information between each other.
% Refer to bursty.py getSimGraph () function

Given a field \(k\) and the time window \(t\), in which the number of events can not be determined in advance.
The two most extreme situations are: events coarse granularity, said the event is equal to the number of Figure \(\mathcal{G}_{k, t} \) in the number of connected components; events finer granularity display, event number equal to \(\mathcal{G}_{k, t} \) the number of points.
To do this, we use the Density to the degree of density of quantum graphs \(2 \#Edge / (\# Node \ cdot (\# Node-1)) \), the more the greater if the edge density in the range of Density in \((0,1] \).
Density can be a good indicator to determine the size indicates the event: too many unrelated phrases to put together an event can not be represented, too fine particle size, such as a single word can represent only part of the event; only in close co-occurrence of the phrase to a reasonable It indicates that the event granularity.
To this end, we have designed events phrase search algorithm \ref{alg:eventKeywordsSearchMethod}: We try to find a reasonable number of spectral clustering Clustering \(n \), let \(n \) from a smaller value ( event corresponds to coarser granularity representation) to start the search, then the most likely cluster cluster size is too large, its performance is the clustering results in one or more small Density indicators; continue to increase the number of clusters \(n \), the event represents reduced size, reduced the size of clusters of clusters, thus making the Density index increases; when all cluster clustering Density indicators are larger than the threshold \(\tau \), the search terminates, returning clustering results \(\mathcal{C}_{k, t}\).
As the above process algorithm \ref{alg:eventKeywordsSearchMethod} description line 2 to line 5, we use in practice \(\rho = 0.6 \).
We call \(\mathcal{C}_{k, t} \) results in each cluster to cluster \textbf{event} phrase.

\textbf{detected events related to micro-blog}
\ \
By algorithm \ref{alg:eventKeywordsSearchMethod} find art \(k \) time window \ \(t \) within the \(| \mathcal{C}_{k, t} | \) events phrase later, you can also further find each event and the corresponding event phrase microblogging.
We looked at the first \(i \) events phrase \(\mathcal{C}_{k, t, i} \),
The phrase based on the number of elements distinguish the event, there are three situations: (1) the phrase event more than two hot words, he said while the event is not a phrase between any two words We have a very strong relationship between the co-occurrence, so just pay attention to the co-occurrence relationship stronger side; (2) event phrase has two hot words; (3) the event is only a hot word in the phrase.
Weibo text length is shorter, not all of the microblogging event will include the phrase \(\mathcal{C}_{k, t, i} \) in all the words.
Such as those on "Apple released the new system mac os lion" event, the event phrase "mac", "os", "lion" does not need to appear in all of the micro-Bo, just check the co-occurrence of a strong relationship between the two words appear together whether in an article in the field \(k \) time window \(t \) micro-Bo: If there is, then added to the events related to the collection \(\mathcal{D}_{k, t, i} \) in.
For the case of a third cluster cluster contains only a hot word, we only need to identify areas \(k \) contains the hot word of all micro-blog, and add the event to the relevant set \(\mathcal{D}_{k, t, i} \) in.
Ultimately, we can get the field \(k \) next time window \(t \) in the event the phrase relating to events microblogging \(\{(\mathcal{C}_{k, t, i}, \mathcal{D}_{k, t, i}) \}_{i=1}^{| \mathcal{C}_{k, t} |} \).
